Spike-and-Slab Generalized Additive Models and Scalable Algorithms for High-Dimensional Data

### 2022-02-25 Manuscript/10-Supplementary.Rmd
Add latex tables to the manuscript
Update supporting document title and authors

---
title: "Supporting Infromation"
output: pdf_document
---

@@

\subsection{Supplementary Information 3: Predictive Performance of Linear Simulations}
\input{Manuscript/Tabs/sim_lnr_gaus_tab.tex}
\clearpage
\input{Manuscript/Tabs/sim_lnr_binom_tab.tex}

>>>>

---
title: Spike-and-Slab Generalized Additive Models and Scalable Algorithms for High-Dimensional Data
subtitle: "Supporting Infromation"
author: Boyi Guo, Byron C. Jaeger, AKM Fazlur Rahman, D. Leann Long, Nengjun Yi
output: 
  pdf_document:
    keep_tex: true
---

@@

\subsection{Supplementary Information 3: Predictive Performance of Linear Simulations}
\input{Tabs/sim_lnr_gaus_tab.tex}
\input{Tabs/sim_lnr_binom_tab.tex}
